Through the eyes of the teacher - Multimodal exploration of expertise differences

### 2024-08-21 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_07_19_MK.Rmd
x paper

# read in data and select and rename relevant columns with transmute 
demo.data <- 
  read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% 
  filter(!LI06_05 == 201) %>% # exclude participant due to missing eye tracking data
  transmute(Group = LI06_05,
            Gender = LI02_01_1,
            Age = LI03_01,
            `Teaching Experience` = LI04_01,
            School_type = LI18,
            Grade = LI16_05,
            Subject = LI10_05,
            Semester = LI11_01,
            Internship = LI13_01,
            `Extracurricular Teaching Experience` = LI14,
            `Secondary Teaching Activities` = LI17
            )

@@

# exclude invalid participants
df_aoi <- df_aoi %>%
  filter(!Participant == 223,
         !Participant == 232)

@@

XXX 223 (ist eine Doppelung der 214) & 232 (enthält NAs) sind fehlerhaft --> Daten nochmal komplett neu ziehen!! XXX

@@

>>>>

# read in data and select and rename relevant columns with transmute 
demo.data <- 
  read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% 
  filter(!LI06_05 == 201,
         !LI06_05 == 223) %>% # exclude participant due to missing eye tracking data
  transmute(Group = LI06_05,
            Gender = LI02_01_1,
            Age = LI03_01,
            `Teaching Experience` = LI04_01,
            School_type = LI18,
            Grade = LI16_05,
            Subject = LI10_05,
            Semester = LI11_01,
            Internship = LI13_01,
            `Extracurricular Teaching Experience` = LI14,
            `Secondary Teaching Activities` = LI17
            )

@@

# exclude invalid participants
df_aoi <- df_aoi %>%
  filter(!Participant == 223)

@@

XXX 223 (ist eine Doppelung der 214) --> Daten nochmal komplett neu ziehen!! XXX

@@

round(d_aver_stud, 2)
